preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-19 Manuscript/manuscript.Rmd
addressed ???

Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods). We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D). Surprisingly, when testing on the K562 cell line, the average AUC increased to 0.837 [??? Wrong number?]. Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.868 [??? Wrong number?], respectively). These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D). The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.

>>>>

Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods). We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D). Surprisingly, when testing on the K562 cell line, the average AUC increased slightly to 0.795. Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.874, respectively). These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D). The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
